Using traffic analysis to identify The Second Generation Onion Router

### 2011-04-17 thesis/results.tex
Revised questions a little, added paragraph to limitations

\begin{table}[H]
  \begin{tabular}{lrrr}
    \toprule
    & True Positive Rate & False Positive Rate & ROC Area \\
    \midrule
    Random Forest\\
    \midrule
    HTTPS & 0.957 & 0.036 & 0.99\\
    HTTP over Tor & 0.937 & 0.037 & 0.986\\
    HTTPS over Tor & 0.977 & 0.003 & 0.999\\
    Weighted Avg. & 0.954 & 0.03 & 0.99\\
    \midrule
    j4.8 With 10 fold cross validation\\
    \midrule
    HTTPS & 0.951 & 0.04 & 0.989\\
    HTTP over Tor & 0.978 & 0.043 & 0.98\\
    HTTPS over Tor & 0.97 & 0.007 & 0.992\\
    Weighted Avg. & 0.964 & 0.018 & 0.986\\
    \midrule
    Random Tree\\
    \midrule
    HTTPS & 0.961 & 0.046 & 0.963\\
    HTTP over Tor & 0.906 & 0.04 & 0.94\\
    HTTPS over Tor & 0.955 & 0.01 & 0.972\\
    Weighted Avg. & 0.941 & 0.037 & 0.957\\
    \midrule
    Adaboost\\
    \midrule
    HTTPS & 0.95 & 0.001 & 0.975\\
    HTTP over Tor & 0.999 & 0.324 & 0.838\\
    HTTPS over Tor & 0 & 0 & 0.777\\
    Weighted Avg. & 0.785 & 0.109 & 0.891\\
    \bottomrule
  \end{tabular}
  \caption{Results}
  \label{table:results}
\end{table}

@@

@@

\begin{enumerate*}
  \item{Can the traffic be classified using automated matching techniques?}

@@

  \item{Do these networks have characteristics that make them readily
  distinguishable using heuristics based matching?}

@@

  \item{Do they have characteristics that make them distinguishable using a
  machine learning technique?}

  \item{How long does a user have to be connected to the network before a
  confident match can be made?}

>>>>

\begin{table}[H]
  \begin{tabular}{lrrr}
    \toprule
    Algorithm & True Positive Rate & False Positive Rate & ROC Area \\
    \midrule
    Random Forest\\
    \midrule
    HTTPS & 0.957 & 0.036 & 0.99\\
    HTTP over Tor & 0.937 & 0.037 & 0.986\\
    HTTPS over Tor & 0.977 & 0.003 & 0.999\\
    Weighted Avg. & 0.954 & 0.03 & 0.99\\
    \midrule
    j4.8 With 10 fold cross validation\\
    \midrule
    HTTPS & 0.951 & 0.04 & 0.989\\
    HTTP over Tor & 0.978 & 0.043 & 0.98\\
    HTTPS over Tor & 0.97 & 0.007 & 0.992\\
    Weighted Avg. & 0.964 & 0.018 & 0.986\\
    \midrule
    Random Tree\\
    \midrule
    HTTPS & 0.961 & 0.046 & 0.963\\
    HTTP over Tor & 0.906 & 0.04 & 0.94\\
    HTTPS over Tor & 0.955 & 0.01 & 0.972\\
    Weighted Avg. & 0.941 & 0.037 & 0.957\\
    \midrule
    Adaboost\\
    \midrule
    HTTPS & 0.95 & 0.001 & 0.975\\
    HTTP over Tor & 0.999 & 0.324 & 0.838\\
    HTTPS over Tor & 0 & 0 & 0.777\\
    Weighted Avg. & 0.785 & 0.109 & 0.891\\
    \bottomrule
  \end{tabular}
  \caption{Results}
  \label{table:results}
\end{table}

@@

The real Tor network consists of over two hundred thousand computer systems,
with over two thousand routers \parencite{TorStatus:2011fk}, all with different
operating systems, different hardware, different configurations and available
bandwidth. All the variables that were controlled for during this experiment
are present in the real network, and may be amplified by it's greater size.
Without further research it is difficult to say if the technique demonstrated
here will apply in the wild.

@@

\begin{enumerate*}
  \item{Can Tor traffic be distinguished from other network traffic that uses
    similar or the same encryption and protocols?}

@@

  \item{Can Tor traffic be identified using automated matching techniques?}

  All the classification algorithms trialled were able to successfully classify
  web browser traffic routed over the simulated Tor network, with the best
  performing algorithm able to correctly classify 95\%.

  The value of this level of accuracy depends on the application. Identifying
  multiple regular connections to the Tor network may provide sufficient
  confidence to classify a system as a Tor node. This could be combined with
  other known properties of the Tor network to increase confidence.

  \item{Does Tor traffic have characteristics that make it readily distinguishable using
    heuristics based matching?}

@@

  \item{Does Tor traffic have characteristics that make it distinguishable using
    machine learning techniques?}

### 2011-04-17 thesis/thesis.tex
Revised questions a little, added paragraph to limitations

\begin{enumerate*}
  \item Can Tor traffic be identified using automated matching techniques?
  \item Does Tor have characteristics that make it readily distinguishable using
    heuristics based matching?
  \item Do they have characteristics that make them distinguishable using
    machine learning techniques?
\end{enumerate*}

>>>>

\begin{enumerate*}
  \item Can Tor traffic be distinguished from other network traffic that uses
    similar or the same encryption and protocols?
  \item Can Tor traffic be identified using automated matching techniques?
  \item Does Tor traffic have characteristics that make it readily distinguishable using
    heuristics based matching?
  \item Does Tor traffic have characteristics that make it distinguishable using
    machine learning techniques?
\end{enumerate*}
